On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2024-01-09 Manuscript/reply.tex
replied to minor comments
Fixed typo in summary
opening paragraph in reply rephased

We thank the editor and the AE for the opportunity to revise the manuscript. and
the two referees for their constructive comments.
We are indebted to the reviewers for pointing out these vital discussion areas,
which have not only enriched the current paper but also charted a clear course
for our subsequent research endeavors.

The manuscript has been
revised accordingly with the following notable changes:
\begin{enumerate}
\item Clarifications of design and more detail examination of results;
\item Reorganization of paragraphs on the Simulation Study, including moving the
Appendix on the Exponential Marginal Distribution Study to the main text;
\item Further discussion of the justification, advantages, and implications of
the Recentered Percentile CI;
\item Additional simulation study using block size 
$l = \lceil 2n^{1/3} \rceil$ in the Appendix.
\end{enumerate}

@@

Thank you for pointing this out. We tried both Wald intervals and exact 
Clopper-Pearson intervals \citep{clopper1934use}, the latter of which
as implemented in the R package \texttt{PropCIs}.\citep{PropCIs}
No major difference between the two was found, which is expected as we
have a large number replication (10,000). Nonetheless, we have
switched to reporting Clopper-Pearson intervals to avoid the potential
undercoverage and discussed this in the third paragraph of the Marginal 
Standard Normal 
Distribution subsection of the Design section.
\jy{Quanlity control the bib entries.}

>>>>

We extend our gratitude to the editor and the Associate Editor for
granting us the opportunity to revise this manuscript. We also want to
express our appreciation to the two referees for their valuable and
constructive comments. The reviewers have highlighted crucial
discussion areas that have not only enhanced the quality of this paper
but have also set a clear direction for our future research
endeavors.

The manuscript has been
revised accordingly with the following notable changes:
\begin{enumerate}
\item Clarifications of design and more detailed examination of results;
\item Reorganization of paragraphs on the Simulation Study, including moving the
Appendix on the Exponential Marginal Distribution Study to the main text;
\item Further discussion of the justification, advantages, and implications of
the Recentered Percentile CI;
\item Additional simulation study using block size 
$l = \lceil 2n^{1/3} \rceil$ in the Appendix.
\end{enumerate}

@@

Thank you for pointing this out. We tried both Wald intervals and exact 
Clopper-Pearson intervals \citep{clopper1934use}, the latter of which
as implemented in the R package \texttt{PropCIs}.\citep{PropCIs}
No major difference between the two was found, which is expected as we
have a large number replication (10,000). Nonetheless, we have
switched to reporting Clopper-Pearson intervals to avoid the potential
undercoverage and discussed this in the third paragraph of the Marginal 
Standard Normal 
Distribution subsection of the Design section.
%\jy{Quanlity control the bib entries.}\mc{addressed}
